---
title: "gg-plot-samples"
author: "Jenna Cohen"
date: "10/20/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Load libraries and establish settings
```{r}
library(tidyverse)
```

## Which day in April 2020 saw the most loans approved in West Virginia? 
### April 28, 2020.

```{r}
#~/Documents/GitHub/data_journalism_2021_fall/labs/lab_09/
wv_ppp_loans<- read_rds("~/Documents/GitHub/jennacohen/gg-plot/lab_09.rds")

wv_loans_approved_april <- wv_ppp_loans %>%
  filter(stringr::str_detect(date_approved, '2020-04')) %>% 
  group_by(date_approved) %>% 
  summarise(
    total_loans=n()
  )

wv_loans_approved_april %>%
  ggplot() + 
  geom_line(aes(x=date_approved, y=total_loans))+
  scale_x_date(date_breaks = "1 day")+
  theme(
    axis.text.x = element_text(angle = 45,  hjust=1)
  )+
  labs(
    title="Loans Approved by Date in April 2020",
    x = "Date Approved",
    y = "Total Loans",
    caption = "Source: SBA PPP loan database"
  ) +
  geom_point(aes(x=date_approved, y=total_loans, ))+
  geom_text(aes(x=date_approved, y=total_loans, label=total_loans, hjust=1.2, vjust=-0.25))

```

## What are the top 10 states that got the most PPP loans per 100,000 people?
```{r}
total_loans_by_state<- read_csv("state_ppp_all.csv")
#rename N and S Dakota to properly join
total_loans_by_state<- total_loans_by_state %>% 
  mutate(state = case_when(
    state == "N Dakota" ~ "North Dakota",
    state == "S Dakota" ~ "South Dakota",
    #this "replaces" existing data that's spelled correctly with itself
    TRUE ~ state
  ))
library(tidycensus)

acs_2019 <- load_variables(2019, "acs5")
#variable name B01001_001
#df with state name and pop from ACS
state_population<- get_acs(geography = "state",
              variables = c(state_pop = "B01001_001"),
              year = 2019) %>% 
  mutate(state_pop = estimate, state = NAME) %>% 
  select(state, state_pop)
#join and find per 100k
states_pop_loans <- state_population %>% 
 right_join(total_loans_by_state) %>% 
  mutate(
    per_100k = (total_ppp_loans/state_pop)*100000
  )%>% 
  arrange(desc(per_100k)) %>%
  head(10)
#states_pop_loans

states_pop_loans %>%
  ggplot() +
  geom_bar(aes(x=reorder(state,per_100k), weight=per_100k), fill="blue")+
  theme(
    axis.text.x = element_text(angle = 45,  hjust=1))+
    labs(
    title="States with Highest PPP Loan Approval per 100,000 People",
    x = "State",
    y = "Loans Approved (per 100,000)",
    caption = "Source: SBA PPP loan database and Census ACS Data"
  ) 

```

## Were there a lot of people who had their loans fully forgiven?  Were there a lot of people who didn't have their loans forgiven? Were there a lot of people who had some of the loan forgiven? 
#### (scatterplot practice)

```{r}
below_25k<- wv_ppp_loans %>% 
  filter(amount <= 25000) %>% 
  mutate(forgiveness_amount = case_when(
    is.na(forgiveness_amount) ~ 0,
    TRUE ~ forgiveness_amount
  ))

below_25k %>% 
  ggplot(aes(x=amount, y=forgiveness_amount))+
  geom_point(size=1)
#Derek's note: it's best practice to put the aes() on the most granular level of the graph, so in this case that would be: ggplot() + geom_point(aes(x=amount,y=forgiveness_amount)) Your way works, but if you're doing a more complicated graph that has multiple elements you want to make sure that you've got the aesthetics on the proper geometric object.
```
