---
title: "kabbage-counties-analysis"
author: "Jenna Cohen"
date: "11/02/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

**codeblock to load appropriate packages and settings** 
```{r}
library(tidyverse)
library(tigris)
```

##The online lender Kabbage, Inc. is featured in the [ProPublica PPP fake farms story](https://www.propublica.org/article/ppp-farms). To show where Kabbage was lending money, I made a county-level map that shows the percentage of loans in each county that were Kabbage loans.

[Chart link] (https://datawrapper.dwcdn.net/JM1yu/1/)
The Kabbage loans are, in general, found more on the east coast. Specifically FL, SC, GA and NJ. On the other hand, CA, NV, ND and NC have 0% Kabbage loans in all of their respective counties. There is no data displayed for DeSoto county, FL. Despite having 4.6% of Kabbage loans, there was no FIPS code matched with their data.
```{r}
#load
kabbage_counties<- read_csv("kabbage_counties.csv")
all_counties<- read_csv("all_counties.csv")

#join, calc percent
kabbage_counties_joined<- all_counties %>% 
  left_join(kabbage_counties, by=c('project_county_name'='project_county_name','project_state'='project_state')) %>% 
  rename( 
    kabbage_loans = total.y,
    all_loans = total.x
    ) %>% 
  mutate(
    percent_kabbage = (kabbage_loans/all_loans)*100
  )
#read in county fips
county_fips<- read_csv("county_fips.csv")

#join with prev df, get rid of zeros
kabbage_counties_fips <- kabbage_counties_joined %>%
  left_join(county_fips, by=c('project_county_name'='match_county','project_state'='state')) %>% 
   mutate(kabbage_loans = case_when(
    is.na(kabbage_loans) ~ 0,
    TRUE ~ kabbage_loans
  )) %>% 
  mutate( percent_kabbage = case_when(
    is.na( percent_kabbage) ~ 0,
    TRUE ~  percent_kabbage
  ))

#export csv
write_csv(kabbage_counties_fips, "kabbage_counties_fips.csv")

```
