---
title: "LGBTQ-character-r-analysis"
author: "Jenna Cohen"
date: "3/20/2022"
output: html_document
---

## Core Dataset

I used the [538 Comic Datasets] (https://github.com/fivethirtyeight/data/tree/master/comic-characters) for my analysis.

## Load libraries
```{r}
#turn off scientific notation
options(scipen=999)
#load tidyverse
library(tidyverse)
#load janitor - clean set names
library(janitor)
#load lubridate - not sure if we'll need
library(lubridate)
#load refinr - not sure if we'll need
library(refinr)
#we'll add to these as we need other libs
```

## Load and Cleaning Data


```{r}
dc<- read_csv("dc_comic_data.csv")
marvel<- read_csv("marvel_comic_data.csv")

#Get rid of Na's in gsm column so it's easier to filter - Jenna
dc<- dc %>% 
  #mutate(
    #type = "comic",
    #publisher = "dc"
  #)
  select(-page_id, -urlslug) %>% 
  clean_names() %>% 
  mutate(gsm = case_when(
    is.na(gsm) ~ "none",
    TRUE ~ gsm
  ))

marvel<- marvel %>% 
  #mutate(
    #type = "comic",
    #publisher = "marvel"
  #)
  select(-page_id, -urlslug) %>% 
  clean_names()%>% 
  mutate(gsm = case_when(
    is.na(gsm) ~ "none",
    TRUE ~ gsm
  ))

#Should probably mutate to add a column in each that says DC or marvel - then join? -Jenna
#tried this and it created a list of 112 million rows??? was expecting 22k -jenna 
#master_list <- marvel %>% 
  #left_join(dc, by=c('type'))
#this isn't working either !!! -jenna
#joined <- rbind(marvel, dc)
```

A compelling aspect of the data I wanted to explore was how the LGBTQ+ community is represented in comics based on the data. 

Comic books are consumed widely across all identities, but I wanted to explore how characters in these comics reflect their audience. I expected to see little representation of LGBTQ+ characters across both universes. My finding, however, was that there is essentially no representation of LGBTQ+ characters- with over 99% of characters in each universe holding a straight identity.

**[Marvel LGBTQ+ Character Visualization]**(https://www.datawrapper.de/_/a7eEt/)

**[DC LGBTQ+ Character Visualization]**(https://www.datawrapper.de/_/ohfLF/)


###### Marvel

```{r}
#end result: count of total GSM & count of majority characters
#for each data set, filter for GSM, count & reverse filter for GSM, count
#also calculate the percentage, dig deeper to see different GSM breakdowns if we were to deem it newsworthy

#gsm characters
marvel_gsm<- marvel %>% 
  filter(gsm != "none")

marvel_gsm_breakdown<- marvel_gsm %>% 
  group_by(gsm) %>% 
  summarise(
    gsm_count = n()
  )
#non_gsm characters
marvel_non_gsm<- marvel %>% 
  filter(gsm == "none")

marvel_non_gsm_breakdown<- marvel_non_gsm %>% 
  group_by(gsm) %>% 
  summarise(
    gsm_count = n()
  )
#total marvel characters for percentage purposes
marvel_characters<- marvel %>% nrow()

marvel_breakdown<- bind_rows(marvel_gsm_breakdown, marvel_non_gsm_breakdown) %>% 
  mutate(
    percent_in_universe = (gsm_count/marvel_characters)*100
  )

write_csv(marvel_breakdown, "marvel_breakdown.csv")

#marvel_gsm_count<- marvel_gsm %>% nrow()
#marvel_non_gsm_count<- marvel_non_gsm %>% nrow()
```

Marvel characters are straight 99.5% of the time, based on the marvel data.

###### DC
```{r}
#gsm characters
dc_gsm<- dc %>% 
  filter(gsm != "none")

dc_gsm_breakdown<- dc_gsm %>% 
  group_by(gsm) %>% 
  summarise(
    gsm_count = n()
  )
#non_gsm characters
dc_non_gsm<- dc %>% 
  filter(gsm == "none")

dc_non_gsm_breakdown<- dc_non_gsm %>% 
  group_by(gsm) %>% 
  summarise(
    gsm_count = n()
  )
#total marvel characters for percentage purposes
dc_characters<- dc %>% nrow()

dc_breakdown<- bind_rows(dc_gsm_breakdown, dc_non_gsm_breakdown) %>% 
  mutate(
    percent_in_universe = (gsm_count/dc_characters)*100
  )

write_csv(dc_breakdown, "dc_breakdown.csv")

#marvel_gsm_count<- marvel_gsm %>% nrow()
#marvel_non_gsm_count<- marvel_non_gsm %>% nrow()
```
DC characters are straight 99.1% of the time, based on the DC data. 
